A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-02-17 main.tex
Updates from Overleaf

%sympathy 富有同情心、慈悲心，靈性高度成熟的醫師，不是只用藥物或手術來治療病患，「他自己本身」就具有療癒效果。
The role of the physician was to be a gentle, sympathetic listener, who could interpret the patient's sympathetic disorder and select the proper remedy to treat it, whether by prescribing placebos to please (influence the emotional states of patients), or medicine to cure the patient's disorder.
placebo effect 安慰劑的研究，拓展了我們對醫病關係的理解，回歸到以病患為中心。
醫療處理的不只是藥物和手術，人更是必須處理的對象，把病患看作一個整體，要掌握身與心的個人特質。
安慰劑效應的研究，最後導向了良好醫病關係的思考，並成為醫生臨床醫術的元素之一：
「醫師開藥時，其實是把自己當藥方開出去」。
安慰劑效應的科學研究，驚人地發現現代西方醫學的不確定性。
The idea of placebo as a diluted but active substance persisted into the 19th century17 but the term also came to mean a physiologically inert substance - bread or lactose, for example.18,19 Inert substances began to be used in comparative clinical trials during the first half of the 19th century,20 but this latter meaning of the term was given particular impetus at the end of the 19th century and the beginning of the 20th century, when inert substances were used as controls in pharmacological experiments.21 This shift in meaning may have reflected the rise of a new emphasis (or even metaphysics) in medicine, in which the molecular make up of an active drug assumed central importance, and any other positive benefits were seen as non-specific, placebo effects.\cite{Kerr2008}

prefrontal lobe 理智腦 意識 正念 杏仁核
「安慰劑」placebo effect，也已經有科學證明，與醫師、病患的意識（前額葉）功能，非常有關係。這也是負責同理心與愛的腦區。
物理作用、信號，雷射針灸

Warburg effect and carcinogenesis
cancer therapy by 患者自癒
Self-Compassion  慈悲
Self-compassion 
除我執
 global self-esteem:
自戀（narcissism）1. Neff, K. D. & Vonk, R. Self-compassion versus global self-esteem: Two different ways of relating to oneself. J. Pers. 77, 23–50 (2009).\cite{Neff2009}

@@

mindfulness and meditation for cancer
情志養生 悲喜憂思苦 七情
%自他不二 心存正念 向內看，解決苦之源
%1.衷心懺悔
%2.真心感謝
%3.誠意祝福
%4.永存善念 慈悲
%5.心無恐懼: 情志養生

@@

the Rstudio Shiny app (https://shiny.rstudio.com) as a web-based tool (named "pvalueTex" ) packaged with our workflow in the future.
with more TCGA features

>>>>

%sympathy 富有同情心、慈悲心，靈性高度成熟的醫師，不是只用藥物或手術來治療病患，「他自己本身」就具有療癒效果。
The role of the physician was to be a gentle, sympathetic listener, who could interpret the patient's sympathetic disorder and select the proper remedy to treat it, whether by prescribing placebos to please (influence the emotional states of patients), or medicine to cure the patient's disorder.
placebo effect 安慰劑的研究，拓展了我們對醫病關係的理解，回歸到以病患為中心。
醫療處理的不只是藥物和手術，人更是必須處理的對象，把病患看作一個整體，要掌握身與心的個人特質。
安慰劑效應的研究，最後導向了良好醫病關係的思考，並成為醫生臨床醫術的元素之一：
「醫師開藥時，其實是把自己當藥方開出去」。
安慰劑效應的科學研究，驚人地發現現代西方醫學的不確定性。
前額葉背側區 (dorsolateral prefrontal cortex)  是形成安慰劑療效的關鍵(PCA「治療關係」的生理學依據)
PCA理論
以心印心 engaging
身心相連 body-mind connection
捨末求本
the anterior cingulate cortex and the dorsolateral prefrontal cortex have been found to be activated by placebo administration.
\cite{Benedetti2005}\cite{Benedetti2011}\cite{Carlino2011}\cite{Bennett2018}
But modern research, especially the results of neuroimaging studies, has shown unequivocally that placebo-induced analgesia is real in the sense that the neural correlates of the sensation of pain are reduced, in the same way that they would be reduced by a decrease in the intensity of a pain-evoking stimulus or by the administration of an analgesic drug\cite{Eippert2009}\cite{Watson2009}. Today, pain researchers are united in the belief that placebo analgesia is real, in the sense that the neural processes that represent pain are reduced\cite{Bennett2018}.
身心靈全人醫療，展現魅力、慈悲心，靈性成熟的醫師，用藥物或手術來治療病患時，
「他自己本身」就具有療癒效果
「把自己當藥方開出去」
#正念 減壓，療癒疼痛\cite{Krummenacher2010}\cite{Bennett2018}、免疫系統、內分泌系統或自律神經系統相關的疾病，以及憂鬱症、焦慮症 
The idea of placebo as a diluted but active substance persisted into the 19th century17 but the term also came to mean a physiologically inert substance - bread or lactose, for example.18,19 Inert substances began to be used in comparative clinical trials during the first half of the 19th century,20 but this latter meaning of the term was given particular impetus at the end of the 19th century and the beginning of the 20th century, when inert substances were used as controls in pharmacological experiments.21 This shift in meaning may have reflected the rise of a new emphasis (or even metaphysics) in medicine, in which the molecular make up of an active drug assumed central importance, and any other positive benefits were seen as non-specific, placebo effects.\cite{Kerr2008}

prefrontal lobe 理智腦 意識 正念 杏仁核
「安慰劑」placebo effect，也已經有科學證明，與醫師、病患的意識（前額葉）功能，非常有關係。這也是負責同理心與愛的腦區。
物理作用、信號，雷射針灸
Therapeutic Relationship
Spirituality
慈悲心 compassion 
同情心 sympathy
同理心 empathy
non-verbal contact
前額葉內側 (medial prefrontal cortex)
額葉底部(orbitofrontal cortex)
治療關係的核心條件: 說好話 眼對眼 engaging 用真心
empowering
(一)雙方有心理的接觸。
(二)當事人正感到焦慮或不一致(incongruence)。 
(三)治療者在治療關係中是一致的、真實的或真誠的。
(四)治療者能夠對當事人表現出無條件的正向關懷。
(五)治療者能夠同理的瞭解當事人的內在，並努力傳達「我懂你的」。
Personhood: Carl Rogers
尋找生命的意義
真誠、能深刻地善解人意
非認知性核心能力
正念止觀(在當下)
人人有自癒能力
真誠 (Genuineness/Validity/Bona Fides)
內在聲音與外在態度一致/明心見性/超越的意識狀態
(Congruence/Consistency)
共情理解(設身處地/同理心/除我執)
(Empathic Understanding of Reference/Track)
無條件關懷(不批判/頓悟)
(unconditional positive regard)
***引導出案主的無條件自我關懷 => 療癒/復原力（resilience）
諮商員的
靈性功力
治療關係
I find that when I am closest to my inner, intuitive self, when I am somehow in touch with the unknown in me, when perhaps I am in a slightly altered state of consciousness, then whatever I do seems to be full of healing. Then simply my presence is releasing and helpful\cite{Rogers1979}.
%當最接近我的內在、直覺的自我，當我與我內在那不知名的角落（the unknown in me）接觸時(靈性)，當我有一些不一樣的意識狀態時（明心見性），我發現，單純只是我的存在（presence）就能鬆綁案主而且具有療效的。
%Rogers, C. R. The Foundations of the Person-Centered Approach. Education 100, 98–107 (1979).
「診後說三句，更勝良帖十方」

Warburg effect and carcinogenesis
cancer therapy by 患者自癒
Mindfullness Meditation help 復原力（resilience）
Self-Compassion  慈悲
Self-compassion 
除我執
 global self-esteem:
自戀（narcissism）1. Neff, K. D. & Vonk, R. Self-compassion versus global self-esteem: Two different ways of relating to oneself. J. Pers. 77, 23–50 (2009).\cite{Neff2009}

@@

mindfulness and meditation for cancer
情志養生 悲喜憂思苦 七情
人俯仰於天地之間
順從四季氣候變化
保養正氣陶冶性情
自我療癒身心靈疾病
%自他不二 心存正念 向內看，解決苦之源
%1.衷心懺悔
%2.真心感謝
%3.誠意祝福
%4.永存善念 慈悲
%5.心無恐懼: 情志養生
每位醫師都可以成為「創傷知情者」
幫助我們身邊的病患， 懂他的心靈創傷
讓他有安全感， 才有機會改變疾病的走向

“每一位患者都有自癒能力， 我們知情之後， 也要逐步讓他本人知情， 看見之後， 在良好的「治療關係」中， 協助他們漸漸找回自己的療癒。（以他們自己的腳步）”
解說：
患者的自癒力就是復原力（resilience),  強調「治療關係」（安全、 信任、 分享權力、 自決） 以及”知情”(暸解過往創傷經驗對自身的影響，進而開始療癒的過程）的重要性。

@@

the Rstudio Shiny app (https://shiny.rstudio.com) as a web-based tool (named "pvalueTex" ) packaged with our workflow in the future.
with more TCGA features (holistic)
Impact of stress on cancer metastasis\cite{Lutgendorf2010}\cite{Moreno-Smith2010}\cite{Du2020}\cite{Xu2021}
cancer initiation under stress\cite{Lutgendorf2010}\cite{Powell2013}
HNSCC\cite{Iftikhar2021}
Adverse psychosocial exposures in early life, namely experiences such as child maltreatment, caregiver stress or depression, and domestic or community violence, have been associated in epidemiological studies with increased lifetime risk of adverse outcomes, including diabetes, heart disease, cancers, and psychiatric illnesses. Additional work has shed light on the potential molecular mechanisms by which early adversity becomes “biologically embedded” in altered physiology across body systems.\cite{Berens2017}
